```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r logo, echo=FALSE}
knitr::include_graphics("images/Questionnaire_header_long.svg")
```

<br><br> <!-- Add two line breaks -->





##  Inclusion criteria for Participants with Bipolar Disorder
 
A a participant of the bipolar group in Ambient-BD you need to meet the following criteria:

* Fluent in English and capable of giving signed, informed consent.
* Aged between 18-50
* Willing and able to install sleep sensors in your bedroom and to wear a wrist worn accelerometer
* Willing to wear polysomnography sensors on four separate nights during the 3-month study duration
* Willing for researchers to visit your home
* Willing to collect multiple saliva samples over 8 hours
*	Have access to a mobile phone and internet.
* Have a diagnosis of BD (DSM5 criteria) with at least one previous manic or hypomanic episode.  
* Willing to have a short online interview with a psychiatrist member of the Ambient-BD team to have your diagnosis confirmed.   
* Clinically euthymic (no episodes of depression, hypomania or mania) for at least three months at the time of enrolement in the study.

Even if you meet the conditions above, you cannot take part if you have:  

* Infectious disease  
* History of allergy or any skin condition that might be exacerbated by exposure to wristwatch straps and electrode paste  
* Chronic disease (eg diabetes, COPD, cancer, heart disease)  
* Intellectual disability  
* Pregnancy  
* Shiftworker  
* Use of recreational drugs or alcohol intake that exceeds HSE recommendations (< 11 drinks per week for women, < 17 for men)  
* Obesity (BMI > 30)  
* Any disability that might affect sleep or the ability to collect saliva samples in dim light or sleep in PSG sensors   
* Intention to travel across a time zone of more than 2h during the study period  



